Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2020-03-26 analysis/paper/Rmd/intro.Rmd
updated intro

@boehm2019thesis and @boehm2019testing argued for complementary roles for mediation analysis and pleiotropy testing in hotspot 
dissection. Here, we clarify this argument by presenting a study of five expression trait 
hotspots in a publicly available data set. At each hotspot, we identify 
a set of local traits that have QTL within the hotspot region. We also identify a set of nonlocal traits with QTL 
arising from the hotspot. We perform pleiotropy tests and mediation analyses for all local-nonlocal trait pairs. 
Graphical summaries of our results enable us to conclude that at least one of the five hotspots is due to multiple QTL, 
while the evidence at the four other hotspots is consistent with a single local trait affecting most or all of the 
nonlocal associated traits. The Chr 5 hotspot

>>>>

@boehm2019thesis and @boehm2019testing argued for complementary roles for mediation analysis and pleiotropy testing in hotspot 
dissection. Here, we clarify this argument by presenting a study of five expression trait 
hotspots in a publicly available data set. At each hotspot, we identify 
a set of local traits that have QTL within the hotspot region. We also identify a set of nonlocal traits with QTL 
arising from the hotspot. We perform pleiotropy tests and mediation analyses for all local-nonlocal trait pairs. 
Graphical summaries of our results enable us to conclude that one of the five hotspots is due to multiple QTL, 
while the evidence at the four other hotspots is consistent with a single local trait affecting most or all of the 
nonlocal associated traits. The Chr 5 hotspot
